The Evolution of Phenotypically Invariant Genetic Networks

### 2017-06-06 handnotes.tex
added: Quant Bio Spec Concept

>>>>

      \begin{example}[Quantitative Biological Species Concept]
        Two populations are said to be different species if they produce low fitness offspring.

        F1s created by crossing externally equivlaent oscillators $A(0)$ and $A(2)$ have an $h_{F_{1}}(t) = e^{t}$, in contrast to both parents with $h_{F_{0}}(t) = \sin(t) + \cos(t)$. The hybrid phenotype is significantly different (it does not oscillate and increases infinitely) despite the phenotypic equivalence of the parents.

        \begin{align*}
          \mathcal{F} \left(h_{F_{0}}\right) &= 1 \\
          \mathcal{F}\left(h_{F_{1}}\right) &= 0
        \end{align*}
      \end{example}
